\LARGE \bf WORKING TITLE: Incorporating User Feedback in Motion Planning for Manipulators

### 2014-09-29 paper2015asml.tex
added a little to the system architecture section. still reworking on some other figures

@@

@@

@@

>>>>

\usepackage{amsmath}
\usepackage{cases}
\usepackage{xspace}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}

%EDITING COMMANDS
\newcommand{\hilight}[1]{\colorbox{red}{#1}}
\newcommand{\todo}{\colorbox{red}{TODO}}

@@

\begin{figure*}
\centering
\begin{subfigure}[b]{0.3\textwidth}
    \includegraphics[trim = 0mm 0mm 0mm 0mm, width=\textwidth]{pictures/drawer_scene}
    \caption{}
    \label{drawer_scene}
  \end{subfigure}%
  ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
%(or a blank line to force the subfigure onto a new line)
  \begin{subfigure}[b]{0.25\textwidth}
    \includegraphics[trim = 0mm 0mm 0mm 0mm, width=\textwidth]{pictures/countertop_scene}
    \caption{}
    \label{fig:countertop_scene}
  \end{subfigure}
  ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
%(or a blank line to force the subfigure onto a new line)
  \begin{subfigure}[b]{0.38\textwidth}
    \includegraphics[trim = 0mm 0mm 0mm 0mm, width=\textwidth]{pictures/industrial_scene}
    \caption{}
    \label{fig:industrial_scene}
  \end{subfigure}
\caption{The scenes used in generating the library of robot motions to collect feedeback for. (a) \emph{Drawer} (b) \emph{Countertop} and (c) \emph{Industrial}}\label{fig:scenes}
\end{figure*}

@@

In order to quickly produce a large number of robot trajectories, the MoveIt benchmarking architecture~\cite{cohen2012generic} was extended with video recording capabilities. Every trajectory was generated by a combination of \emph{scenes}, \emph{queries}, and \emph{planners}. In this paper, our trajectories are planned in three distinct scenes (shown in~\ref{fig:scenes}) which the robot can interact in: a kitchen (\emph{Countertop}), an industrial workbench (\emph{Industrial}) and a drawer on a table (\emph{Drawer}).

@@

The surveys were presented to users of Amazon Mechanical Turk, who would be presented with a set of demographic questions, a video, and the four scales to rate the robot's motion on the basis of elegance, efficency, smoothness and overall impression. Additionally a control question was presented with another video asking the participant about the robot's action in the accompanying video. This served as the first satisficing trap to ensure that participants were truthfully attempting the survey.

Each participant was allowed to provide feedback no more than once for each of the trajectories generated by the survey design.
